---
title: "ExamplePackage Vignette"
author: "Steven J. Mack"
date: "8/28/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
* Package Version: 0.1.0.9000

## Overview

This is an example R package created for the **UCSF R Packages Workshop**. 

This package includes two functions -- `powers()` and `factors()` -- and `primes`, a dataset of the first 10008 prime numbers.

## Functions

### Powers

The `powers()` function returns the value of `num` raised to `exp`. Both `num` and `exp` are expected to be numeric values. If `num` is not provided, a warning message will be returned. The default value of `exp` is 2. 

For example:

```{r example1}
library("ExamplePackage")
powers(27,0.5)
powers(27,2)
powers(primes$p[3],primes$p[6])
powers()
```
### Factors

The `factors()` function returns a vector containing all factors of `int`, a positive integer. If `int` is negative, a warning message will be returned. 

For example:
```{r example2}
library("ExamplePackage")
factors(1234)
facts <- factors(1239)
facts
factors(-1239)
factors(primes$p[3]*primes$p[6])
```
End of Vignette
